Bayesian MCMC diagnostics and summarization using Tracer 1.6

### 2017-02-03 manuscript/tracer16.tex
mv figures into manuscript, use previous figures folder for Markdown files
3 trace types & conditional posterior distribution

\section{Motivation:}
Computational evolutionary biology, statistical phylogenetics and coalescent-based population genetics are becoming increasingly central to the analysis and understanding of molecular sequence data. 
\section{Results:}
We describe here a software package, Tracer version 1.6, which ... 
\section{Availability:}
Tracer is open-source under the GNU lesser general public license and available at \url{http://beast-mcmc.googlecode.com}  and  \href{http://tree.ed.ac.uk/software/tracer}{\url{http://tree.ed.ac.uk}}.

@@

New features:
\begin{itemize}
\item Kernel density estimates
\item HME
\item AICM
\end{itemize}

@@

\begin{figure}[H]
\includegraphics[width=.5\textwidth]{../figures/gopher-log.png}  
\caption{The }
\label{fig:front:page}
\end{figure}

\begin{figure}[H]
\includegraphics[width=.5\textwidth]{../figures/estimates.pdf}  
\caption{The estimates}
\label{fig:estimates}
\end{figure}

\begin{figure}[H]
\includegraphics[width=.5\textwidth]{../figures/comp-95HPD.pdf}  
\caption{The comparison of  95\% HPD intervals from multi-trace}
\label{fig:comp95HPD}
\end{figure}

\begin{figure}[H]
\includegraphics[width=.5\textwidth]{../figures/trace.pdf}  
\caption{The trace}
\label{fig:trace}
\end{figure}

@@

>>>>

\section{Motivation:}
Computational evolutionary biology, statistical phylogenetics and coalescent-based population genetics are becoming increasingly central to the analysis and understanding of molecular sequence data. 
\section{Results:}
We describe here a software package, Tracer version 1.6, which ... 
\section{Availability:}
Tracer is open-source under the GNU lesser general public license and available at 
\url{http://beast-mcmc.googlecode.com}  %TODO \url{http://github.com/beast-dev/tracer}
and  \href{http://tree.ed.ac.uk/software/tracer}{\url{http://tree.ed.ac.uk}}.

@@

New features:
\begin{itemize}
\item Three trace types: real, integer, string
\item Kernel density estimates
\item HME
\item AICM
\end{itemize}

@@

\begin{figure}[H]
\includegraphics[width=.5\textwidth]{./figures/gopher-log.png}  
\caption{The }
\label{fig:front:page}
\end{figure}

\begin{figure}[H]
\includegraphics[width=.5\textwidth]{./figures/estimates.pdf}  
\caption{The estimates}
\label{fig:estimates}
\end{figure}

\begin{figure}[H]
\includegraphics[width=.5\textwidth]{./figures/comp-95HPD.pdf}  
\caption{The comparison of  95\% HPD intervals from multi-trace}
\label{fig:comp95HPD}
\end{figure}

\begin{figure}[H]
\includegraphics[width=.5\textwidth]{./figures/trace.pdf}  
\caption{The trace}
\label{fig:trace}
\end{figure}

\begin{figure}[H]
\includegraphics[width=.5\textwidth]{./figures/jointPrInt.png}  
\caption{The Joint probability table of two integer traces}
\label{fig:int:jointpr}
\end{figure}

@@

Fairly general solution to looking at conditional posterior distributions;

Specifically, support for BSSVS forms of model averaging, in which some parameters are only in the likelihood when their submodel is "indicated" by some indicator function that is usually a discrete, integer or boolean variable. In that case the posterior of the parameter should not include the states when it was sampled only in the prior because the submodel it belonged to was "turned off". This is relevant for EBSP, Random Local Clocks model, microsatellite model averaging and relaxed clock model averaging methods all from my group in last couple of years. Also relevant for BSSVS in phylogeography as well depending on how the state is logged.
